% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{hyperref}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.5in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{-7pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-15pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

  \textbf{{\Large Taylor E. Grubbs}} & \textbf{\today} \\
  \texttt{tegrubbs@ncsu.edu} \\
  \texttt{(919)368-5087}  \\
  \href{https://www.researchgate.net/profile/Taylor-Grubbs}{ResearchGate: researchgate.net/profile/Taylor-Grubbs} \\
  \href{https://github.com/tedgrubbs}{Github: github.com/tedgrubbs}  \\
  \href{https://www.linkedin.com/in/taylor-grubbs/}{Linkedin: linkedin.com/in/taylor-grubbs/}

\end{tabular*}


%\begin{flushleft}
%\textit{}

%\end{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{North Carolina State University}{Raleigh, NC}{Ph.D. Student in Nuclear Engineering}{2023-Present}

\item
	\ressubheading{North Carolina State University}{Raleigh, NC}{M.S. Physics}{2019}
	

\item
	\ressubheading{University of North Carolina at Greensboro}{Greensboro, NC}{B.S. Physics}{2016}
	\begin{itemize}
		\resitem{Graduated on Chancellor's List with Minors in Chemistry and Mathematics}
		\resitem{Inducted into Phi Beta Kappa Honors Society}
	\end{itemize}


\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}
  \resitem{Python, C/C++, Scientific Computing, GNU/Linux, PyTorch, Rust, Bash, Git, LaTeX, Technical Writing}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Research and Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
  \ressubheading{North Carolina State University}{Raleigh, NC}{Graduate Research Assistant}{January 2023 - Present}
  

\item
  \ressubheading{Lawrence Livermore National Laboratory}{Livermore, CA}{Defense Science and Technology Intern}{May 2023 - August 2023}
  \begin{itemize}
    \resitem{Implemented in-line detector modeling capability in a Monte Carlo Thermal Radiative Transport (TRT) code.}
    \resitem{Capability was verified on multiple test problems.}
    \resitem{Presented a poster and exit talk to describe work to other interns and staff members.}        
  \end{itemize}
  
\item
	\ressubheading{Invisible Technologies, Inc}{San Francisco, CA (Remote)}{AI Data Expert}{October 2022 - December 2022}
	\begin{itemize}
      \resitem{Acted as subject matter expert for AI dataset creation.}
      \resitem{Worked with other experts to organize AI model testing curriculum.}
	  \resitem{Improved models through adversarial testing.}
      
      
	\end{itemize}

\item
	\ressubheading{ExoCrypt Investments, LLC}{Raleigh, NC}{Data Scientist and Machine Learning Engineer}{August 2020 - August 2022}
	\begin{itemize}
      \resitem{Built a framework in Python and PyTorch for the rapid training and testing of deep neural networks.}
      \resitem{Used ideas adapted from image classification literature to discover unique insights about market data.}
      \resitem{Built several Python scripts to aid data annotation performed by other team members.}
      \resitem{Produced performant models that could search for rare patterns within millions of hours of market data.}
      \resitem{Performed extensive model validation to ensure expected results across different end-user devices.}
      
	\end{itemize}



\item
	\ressubheading{NCSU Department of Physics}{Raleigh, NC}{Lead Teaching Assistant}{August 2018 - December 2019}
	\begin{itemize}
      \resitem{Instructed General Physics labs in electricity/magnetism and Newtonian Mechanics for undergraduate students.}
      \resitem{As Lead TA was responsible for the instruction of lab lesson plans to other TAs.}
      \resitem{Received consistently high reviews from students regarding my communication and knowledge of the subject matter.}
	\end{itemize}
	
\item
	\ressubheading{NCSU Department of Physics}{Raleigh, NC}{Brief Research Work}{December 2018 - April 2019}
	\begin{itemize}
      \resitem{Simulated the transport of ultracold neutrons through experimental designs using a Monte Carlo code written in C++.}
      \resitem{Performed data analysis using the CERN Root library.}
      \resitem{After leaving the project I helped instruct group members to bring them up to speed on the code's inner working so that they could continue the project.}
    
	\end{itemize}

\item
	\ressubheading{CData Software, Inc.}{Chapel Hill, NC}{Software Developer/Technical Support Representative}{March 2017 - July 2018}
	\begin{itemize}
      \resitem{Helped connect customers' databases like SQL, MySQL, etc to business intelligence sources like Salesforce, Dynamics 365, QuickBooks and dozens more.}
      \resitem{Worked at fast pace with customers and team members to solve issues quickly.}
      \resitem{Debugging and development in Java and C\#.}
      
	\end{itemize}

\item
	\ressubheading{UNCG Department of Chemistry and Biochemistry}{Greensboro, NC}{Undergraduate Researcher - Physical Chemistry}{January 2014 - December 2016}
	\begin{itemize}
      \resitem{Programmed microcontroller for solar tracking of a linear Fresnel refelector.}
      \resitem{Managed the operation of laser-induced photodissociation experiments of ozone with carbon tetrachloride to create chlorine monoxide.}
      \resitem{Programmed Lua scripts in SIMION for the simulation of molecular transport to guide design of an electric molecular trap.}
	\end{itemize}

\item
	\ressubheading{UNCG Department of Physics and Astronomy}{Greensboro, NC}{Undergraduate Teaching Assistant - General Physics}{January 2016 - December 2016}
	\begin{itemize}
      \resitem{Aided the in-class instruction of advanced general physics classes.}    
	\end{itemize}
	
\item
	\ressubheading{Grubbs Tree and Shrub Care}{Broadway, NC}{General Laborer}{2008 - 2016 (Summers)}
	\begin{itemize}
      \resitem{Performed general landscape maintentance and installation tasks.}     
	\end{itemize}

\end{itemize}

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Certifications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item 
	CompTia \textbf{Security+}, 2022
	
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Extra}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Side Projects}{}{Personal code and writing projects - see Github link at top.}{}
	\begin{itemize}
	  \resitem{Logging system in Rust.}
          \resitem{Navier-Stokes Fluid simulation in C++.}          
          \resitem{Object detection with neural networks.}
	\end{itemize}



\end{itemize}

\end{document}
